Manuscript analyses

### 2022-03-17 Manuscript analyses.Rmd
Add tables

```{r load}
path <- fs::path("","Volumes","Peres_Research", "Myeloma", "Cytopenias")

Characteristics <-
  readxl::read_xlsx(paste0(path,"/CytopeniaManuscriptData_3.16.22.xlsx"),
                    sheet = "Characteristics", skip = 1, n_max = 54) %>% 
  mutate(MRN = as.character(MRN),
         MRN = coalesce(MRN, PT))
Counts <-
  readxl::read_xlsx(paste0(path,"/CytopeniaManuscriptData_3.16.22.xlsx"),
                    sheet = "Counts") %>% 
  mutate(MRN = as.character(MRN),
         MRN = coalesce(MRN, PT))
Infections <-
  readxl::read_xlsx(paste0(path,"/CytopeniaManuscriptData_3.16.22.xlsx"),
                    sheet = "Infections") %>% 
  mutate(MRN = as.character(MRN),
         MRN = coalesce(MRN, PT))
Support <-
  readxl::read_xlsx(paste0(path,"/CytopeniaManuscriptData_3.16.22.xlsx"),
                    sheet = "Support") %>% 
  mutate(MRN = as.character(MRN),
         MRN = coalesce(MRN, PT))
Pneumo_titers <-
  readxl::read_xlsx(paste0(path,"/CytopeniaManuscriptData_3.16.22.xlsx"),
                    sheet = "Pneumo Titers") %>% 
  mutate(MRN = as.character(MRN))
Other_titers <-
  readxl::read_xlsx(paste0(path,"/CytopeniaManuscriptData_3.16.22.xlsx"),
                    sheet = "Other Titers") %>% 
  mutate(MRN = as.character(MRN))
```

@@

@@

@@

  mutate(`ECOG at LD (at baseline visit)` = case_when(
    `ECOG at LD (at baseline visit)` == 0 | 
      `ECOG at LD (at baseline visit)` ==1 ~ "0-1"

@@

  )

@@

# day 30 + MRD for figure
#table(tct$day30_response_revised, tct$MRD_status, useNA= "ifany")
#table(tct$day30_response_revised, tct$day30_response, useNA= "ifany")
#tct$ORR_MRD <- case_when(#tct$day30_response_revised== "SD" ~ "SD",
                         #tct$day30_response_revised== "PD" ~ "PD",
                         #tct$day30_response_revised== "MR" ~ "MR",
#                         tct$day30_response_revised== "PR" ~ "PR",
                         #tct$day30_response_revised== "PR" & tct$MRD_status== "Positive" ~ "PR and MRD-positive",
                         #tct$day30_response_revised== "PR" & is.na(tct$MRD_status) ~ "PR and MRD unknown",
#                         tct$day30_response_revised== "sCR" & tct$MRD_status== "Negative" ~ "sCR and MRD-negative",
#                         tct$day30_response_revised== "sCR" & tct$MRD_status== "Positive" ~ "sCR and MRD-positive")
#table(tct$ORR_MRD)
## Labeling
var_label(cart1) <- list(Age = "Patient Age", agecat = "Patient Age - Categories", bmicat = "BMI at apheresis - Normal, Overweight, Obese", 
                         tumor_burden = "Tumor burden", proteasome = "Refractory to Proteasome Inhibitors", 
                         immuno = "Refractory to Immunomodulators", doubleref = "Double refractory", 
                         tripleref= "Triple refractory", pentaref= "Penta refractory",
                         bmicat2 = "BMI at apheresis - Normal vs. Overweight/Obese", CRS_any = "Any CRS", CRS_gradecat = "CRS Grade", 
                         ICANS_any = "Any ICANS", ICANS_gradecat = "ICANS Grade", cyto= "High risk cytogenetics", 
                         `ECOG > or = 2? (Yes=1, No=0)` = "Deletion 17p at Infusion", 
                         `t(4:14) prior to CAR-T infusion (yes=1, no=0)` = "t(4:14) at Infusion", `t(14:16) prior to CAR-T infusion (yes=1, no=0)` = "t(4:16) at Infusion", 
                         `Prior auto SCT (yes=1, no=0)` = "Prior auto SCT", `Extramedullary Disease? (yes=1, no=0)` = "Extramedullary disease", dara= "Refractory to Daratumumab")

@@

## Table 1. Patient baseline characteristics
```{r}
selected <- cart1 %>% 
  select(Age, agecat, Sex, `BMI at apheresis`, bmicat, bmicat2, `Extramedullary Disease? (yes=1, no=0)`, tumor_burden, `ECOG at LD (at baseline visit)`, `R-ISS at CAR-T Infusion`, `ECOG > or = 2? (Yes=1, No=0)`, `t(4:14) prior to CAR-T infusion (yes=1, no=0)`, `t(14:16) prior to CAR-T infusion (yes=1, no=0)`, cyto, `Bridging Therapy (Yes=1, No=0)`, `Number of prior lines of therapy`, `Prior auto SCT (yes=1, no=0)`, immuno, proteasome, dara, doubleref, tripleref, pentaref, CRS_any, CRS_gradecat, `Duration of CRS (days)`, ICANS_any, ICANS_gradecat, `Duration of ICANS (days)`, `Infection (yes, no)`, `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`, 
                             # `Baseline CRP`, `Max CRP`, `Baseline Ferritin`, `Max Ferritin`, `Cell Dose (million cells)`, 
                             # `LDH at Baseline`, 
                             `LDH day +30`, `LDH day +90`#, 
                             # `B2 Microglobulin at Baseline`, `Day 30 B2 Microglobulin`, `Day 90 B2 Microglobulin`, `Cyclophosphamide Dose (mg)`, `Cyclophosphamide Actual Dose (mg/m2)`, `Fludarabine Total Dose (mg)`, `Fludarabine Actual Dose (mg/m2)`, `Fludarabine Dose Reduction`
                             )
# write.csv(selected,"/Volumes/Peres_Research/Myeloma/CART/selected_data.csv", row.names = TRUE)
selected %>% 
  tbl_summary(
            statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
            digits = all_continuous() ~ 1) %>% 
  bold_labels() %>% add_stat_label() %>% 
             #modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
  # use `modify_footnote(everything() ~ NA, abbreviation = TRUE)` to delete abbrev. footnotes
  modify_footnote(update = everything() ~ NA)
```

<!-- Age (years)	 -->
<!--      Median (range)	 -->
<!--      60 – n (%)	 -->
<!-- Male sex – n (%)	 -->
<!-- Extramedullary disease – n (%)	 -->
<!-- High marrow burden (≥50%) – n (%)	 -->
<!-- ECOG performance status at lymphodepletion – n (%)	 -->
<!--      0	 -->
<!--      1	 -->
<!--      2	 -->
<!--      3	 -->
<!-- R-ISS stage – n (%)	 -->
<!--      I	 -->
<!--      II	 -->
<!--      III	 -->
<!--      Unknown	 -->
<!-- High-risk cytogenetics – n (%)	 -->
<!--      del(17p)	 -->
<!--      t(4;14)	 -->
<!--      t(14;16)	 -->
<!--      Unknown	 -->
<!-- Bridging therapy – n (%)	 -->
<!-- Prior anti-myeloma regimens – median (range)	 -->
<!--      Prior autoSCT – n (%)	 -->
<!--      Prior alloSCT – n (%)	 -->
<!--      Prior BCMA-directed therapy – n (%)	 -->
<!-- Refractory status – n (%)	 -->
<!--      Immunomodulatory agent	 -->
<!--      Proteasome inhibitor	 -->
<!--      Daratumumab	 -->
<!--      Double-refractory disease	 -->
<!--      Triple-refractory disease	 -->
<!--      Penta-refractory disease	 -->
<!-- Eligible for KarMMa 1 trial at apheresis – n (%)	 -->

## Table 2. Clinical outcomes

<!-- CRS maximum grade – n (%)	 -->
<!--      0	 -->
<!--      1	 -->
<!--      2	 -->
<!--      3	 -->
<!--      4	 -->
<!--      5	 -->
<!-- Time to CRS onset (days) – median (range)	 -->
<!-- Time to maximum severity CRS (days) – median (range)	 -->
<!-- Duration of CRS (days) – median (range)	 -->
<!-- ICANS maximum grade – n (%)	 -->
<!--      0	 -->
<!--      1	 -->
<!--      2	 -->
<!--      3	 -->
<!--      4	 -->
<!--      5	 -->
<!-- Time to ICANS onset (days) – median (range)	 -->
<!-- Time to maximum severity ICANS (days) – median (range)	 -->
<!-- Duration of ICANS (days) – median (range)	 -->
<!-- Treatment for toxicity – n (%)	 -->
<!--      Steroid use	 -->
<!--      Tocilizumab use	 -->
<!--      Anakinra use	 -->
<!-- Day 30 response – n (%)	 -->
<!--      ORR	 -->
<!--      CR or sCR	 -->
<!--           MRD negative	 -->
<!--      VGPR	 -->
<!--      PR	 -->
<!-- Day 90 response – n (%)	 -->
<!--      ORR	 -->
<!--      CR or sCR	 -->
<!--           MRD negative	 -->
<!--      VGPR	 -->
<!--      PR	 -->
<!-- Best response in first 90 days – n (%)	 -->
<!--      CR or sCR	 -->
<!--           MRD negative	 -->
<!--      VGPR	 -->
<!--      PR	 -->

For responses make denominator evaluable patients
Patient who died or was lost to follow-up or had non-secretory disease would not be evaluable

## Table 3. Bone marrow biopsy findings

<!-- 	Baseline (n=52)	Day 30 (n=44)	Day 90 (n=32) -->
<!-- Marrow cellularity – n (%)			 -->
<!--      Hypocellular			 -->
<!--      Normocellular			 -->
<!--      Hypercellular			 -->
<!--      Variable			 -->
<!-- Marrow cellularity (%) – median (range)			 -->
<!-- % CD138 positive by IHC – median (range)			 -->
<!-- Fibrosis grade – median (range)			 -->
<!-- Dysplasia present – n (%)			 -->

## Table 4. Supportive therapies and engraftment

<!-- Granulocyte colony stimulating factor (G-CSF)	 -->
<!--      G-CSF administered – n (%)	 -->
<!--      First day of G-CSF – median (range)	 -->
<!--      Last day of G-CSF – median (range)	 -->
<!-- CD34 stem cell boost	 -->
<!--      Stem cell boost administered – n (%)	 -->
<!--      Day of stem cell boost – median (range)	 -->
<!--      Dose of stem cell boost (million cells) – median (range)	 -->
<!-- Engraftment day – median (range)	 -->
<!-- Transfusions post-CART – n (%)	 -->
<!--      RBC transfusion within 7 days	 -->
<!--      Plt transfusion within 7 days	 -->
<!--      RBC transfusion >7 days	 -->
<!--      Plt transfusion >7 days	 -->
<!-- Intravenous immunoglobulin (IVIG)	 -->
<!--      IVIG administered – n (%)	 -->
<!--      First day of IVIG – median (range)	 -->
<!--      Last day of IVIG – median (range)	 -->

## Table S1. Apheresis and product characteristics

<!-- Collection goal (TBV) – median (range)	 -->
<!-- Whole blood processed (mL) – median (range)	 -->
<!-- Total blood volume processed (mL) – median (range)	 -->
<!-- Access type – n (%)	 -->
<!--      Non-tunneled central venous catheter	 -->
<!--      Peripheral line	 -->
<!--      Other	 -->
<!-- Final collection volume (mL) – median (range)	 -->
<!-- Run time (minutes) – median (range)	 -->
<!-- Time from apheresis to product infusion (days) – median (range)	 -->
<!-- Total bags infused – median (range)	 -->
<!-- Total dose volume (mL) – median (range)	 -->
<!-- Total cell dose (million cells) – median (range)	 -->

## Table S2. Cytopenias following ide-cel

<!-- 	Apheresis	Day -5	Day 0	Day 7	Day 14	Day 21	Day 30	Day 90 -->
<!-- Leukopenia – n (%)								 -->
<!--      Any grade								 -->
<!--      Grade 3+								 -->
<!-- Neutropenia – n (%)								 -->
<!--      Any grade								 -->
<!--      Grade 3+								 -->
<!-- Anemia – n (%)								 -->
<!--      Any grade								 -->
<!--      Grade 3+								 -->
<!-- Thrombocytopenia – n (%)								 -->
<!--      Any grade								 -->
<!--      Grade 3+								 -->

## Table S3. Patient characteristics by grade 3+ cytopenia at Day 30

## Table S3. Patient characteristics by grade 3+ cytopenia at Day 90

(Similar to above)

>>>>

```{r load}
# path <- fs::path("","Volumes","Peres_Research", "Myeloma", "Cytopenias")

Characteristics <-
  readxl::read_xlsx("./CytopeniaManuscriptData_3.16.22.xlsx",
                    sheet = "Characteristics", skip = 1, n_max = 54) %>% 
  mutate(MRN = as.character(MRN),
         MRN = coalesce(MRN, PT))
Counts <-
  readxl::read_xlsx("./CytopeniaManuscriptData_3.16.22.xlsx",
                    sheet = "Counts") %>% 
  mutate(MRN = as.character(MRN),
         MRN = coalesce(MRN, PT))
Infections <-
  readxl::read_xlsx("./CytopeniaManuscriptData_3.16.22.xlsx",
                    sheet = "Infections") %>% 
  mutate(MRN = as.character(MRN),
         MRN = coalesce(MRN, PT))
Support <-
  readxl::read_xlsx("./CytopeniaManuscriptData_3.16.22.xlsx",
                    sheet = "Support",
                    range = "A1:U53") %>% 
  mutate(MRN = as.character(MRN),
         MRN = coalesce(MRN, PT))
Pneumo_titers <-
  readxl::read_xlsx("./CytopeniaManuscriptData_3.16.22.xlsx",
                    sheet = "Pneumo Titers") %>% 
  mutate(MRN = as.character(MRN))
Other_titers <-
  readxl::read_xlsx("./CytopeniaManuscriptData_3.16.22.xlsx",
                    sheet = "Other Titers") %>% 
  mutate(MRN = as.character(MRN))
```

@@

  mutate(male_sex = case_when(
    Sex == "M"                                                    ~ 1,
    TRUE                                                          ~ 0

@@

              "Prior Allo SCT (Yes=1, No=0)",
              "Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)",

@@

  # mutate(`ECOG at LD (at baseline visit)` = case_when(
  #   `ECOG at LD (at baseline visit)` == 0 | 
  #     `ECOG at LD (at baseline visit)` == 1                       ~ "0-1",
  #   TRUE                                                          ~ `ECOG at LD (at baseline visit)`

@@

  # mutate(best_response = ) %>% 
  mutate(Leukopenia_apheresis = case_when(
    `WBC apheresis` < 4                                           ~ "YES"
  mutate(`Leukopenia_-5d` = case_when(
    `WBC day -5 (k/ul)` < 4                                        ~ "YES"
  mutate(`Leukopenia_0d` = case_when(
    `WBC day 0 (k/uL)` < 4                                        ~ "YES"
  mutate(`Leukopenia_7d` = case_when(
    `WBC day +7` < 4                                              ~ "YES"
  mutate(`Leukopenia_14d` = case_when(
    `WBC day +14` < 4                                             ~ "YES"
  mutate(`Leukopenia_21d` = case_when(
    `WBC day +21` < 4                                             ~ "YES"
  mutate(`Leukopenia_30d` = case_when(
    `WBC day +30` < 4                                             ~ "YES"
  mutate(`Leukopenia_90d` = case_when(
    `WBC day +90` < 4                                             ~ "YES"
  mutate(gr3_Leukopenia_apheresis = case_when(
    `WBC apheresis` < 2                                           ~ "YES"
  mutate(`gr3_Leukopenia_-5d` = case_when(
    `WBC day -5 (k/ul)` < 2                                       ~ "YES"
  mutate(`gr3_Leukopenia_0d` = case_when(
    `WBC day 0 (k/uL)` < 2                                        ~ "YES"
  mutate(`gr3_Leukopenia_7d` = case_when(
    `WBC day +7` < 2                                              ~ "YES"
  mutate(`gr3_Leukopenia_14d` = case_when(
    `WBC day +14` < 2                                             ~ "YES"
  mutate(`gr3_Leukopenia_21d` = case_when(
    `WBC day +21` < 2                                             ~ "YES"
  mutate(`gr3_Leukopenia_30d` = case_when(
    `WBC day +30` < 2                                             ~ "YES"
  mutate(`gr3_Leukopenia_90d` = case_when(
    `WBC day +90` < 2                                             ~ "YES"

  mutate(Neutropenia_apheresis = case_when(
    `ANC apheresis` < 1.8                                           ~ "YES"
  )) %>% 
  mutate(`Neutropenia_-5d` = case_when(
    `ANC day -5 (k/ul)` < 1.8                                        ~ "YES"
  )) %>% 
  mutate(`Neutropenia_0d` = case_when(
    `ANC day 0 (k/uL)` < 1.8                                        ~ "YES"
  )) %>% 
  mutate(`Neutropenia_7d` = case_when(
    `ANC day +7` < 1.8                                              ~ "YES"
  )) %>% 
  mutate(`Neutropenia_14d` = case_when(
    `ANC day +14` < 1.8                                             ~ "YES"
  )) %>% 
  mutate(`Neutropenia_21d` = case_when(
    `ANC day +21` < 1.8                                             ~ "YES"
  )) %>% 
  mutate(`Neutropenia_30d` = case_when(
    `ANC day +30` < 1.8                                             ~ "YES"
  )) %>% 
  mutate(`Neutropenia_90d` = case_when(
    `ANC day +90` < 1.8                                             ~ "YES"
  )) %>% 
  mutate(gr3_Neutropenia_apheresis = case_when(
    `ANC apheresis` < 1                                           ~ "YES"
  )) %>% 
  mutate(`gr3_Neutropenia_-5d` = case_when(
    `ANC day -5 (k/ul)` < 1                                        ~ "YES"
  )) %>% 
  mutate(`gr3_Neutropenia_0d` = case_when(
    `ANC day 0 (k/uL)` < 1                                        ~ "YES"
  )) %>% 
  mutate(`gr3_Neutropenia_7d` = case_when(
    `ANC day +7` < 1                                              ~ "YES"
  )) %>% 
  mutate(`gr3_Neutropenia_14d` = case_when(
    `ANC day +14` < 1                                             ~ "YES"
  )) %>% 
  mutate(`gr3_Neutropenia_21d` = case_when(
    `ANC day +21` < 1                                             ~ "YES"
  )) %>% 
  mutate(`gr3_Neutropenia_30d` = case_when(
    `ANC day +30` < 1                                             ~ "YES"
  )) %>% 
  mutate(`gr3_Neutropenia_90d` = case_when(
    `ANC day +90` < 1                                             ~ "YES"
  )) %>%

  mutate(Anemia_apheresis = case_when(
    `Hb apheresis` < 11.4                                           ~ "YES"
  )) %>% 
  mutate(`Anemia_-5d` = case_when(
    `Hb day -5 (k/ul)` < 11.4                                        ~ "YES"
  )) %>% 
  mutate(`Anemia_0d` = case_when(
    `Hb day 0 (k/uL)` < 11.4                                        ~ "YES"
  )) %>% 
  mutate(`Anemia_7d` = case_when(
    `Hb day +7` < 11.4                                              ~ "YES"
  )) %>% 
  mutate(`Anemia_14d` = case_when(
    `Hb day +14` < 11.4                                             ~ "YES"
  )) %>% 
  mutate(`Anemia_21d` = case_when(
    `Hb day +21` < 11.4                                             ~ "YES"
  )) %>% 
  mutate(`Anemia_30d` = case_when(
    `Hb day +30` < 11.4                                             ~ "YES"
  )) %>% 
  mutate(`Anemia_90d` = case_when(
    `Hb day +90` < 11.4                                             ~ "YES"
  )) %>% 
  mutate(gr3_Anemia_apheresis = case_when(
    `Hb apheresis` < 8                                           ~ "YES"
  )) %>% 
  mutate(`gr3_Anemia_-5d` = case_when(
    `Hb day -5 (k/ul)` < 8                                        ~ "YES"
  )) %>% 
  mutate(`gr3_Anemia_0d` = case_when(
    `Hb day 0 (k/uL)` < 8                                        ~ "YES"
  )) %>% 
  mutate(`gr3_Anemia_7d` = case_when(
    `Hb day +7` < 8                                              ~ "YES"
  )) %>% 
  mutate(`gr3_Anemia_14d` = case_when(
    `Hb day +14` < 8                                             ~ "YES"
  )) %>% 
  mutate(`gr3_Anemia_21d` = case_when(
    `Hb day +21` < 8                                             ~ "YES"
  )) %>% 
  mutate(`gr3_Anemia_30d` = case_when(
    `Hb day +30` < 8                                             ~ "YES"
  )) %>% 
  mutate(`gr3_Anemia_90d` = case_when(
    `Hb day +90` < 8                                             ~ "YES"
  )) %>%

  mutate(Thrombocytopenia_apheresis = case_when(
    `Plt apheresis` < 143                                           ~ "YES"
  )) %>% 
  mutate(`Thrombocytopenia_-5d` = case_when(
    `Plt day -5 (k/ul)` < 143                                        ~ "YES"
  )) %>% 
  mutate(`Thrombocytopenia_0d` = case_when(
    `Plt day 0 (k/uL)` < 143                                        ~ "YES"
  )) %>% 
  mutate(`Thrombocytopenia_7d` = case_when(
    `Plt day +7` < 143                                              ~ "YES"
  )) %>% 
  mutate(`Thrombocytopenia_14d` = case_when(
    `Plt day +14` < 143                                             ~ "YES"
  )) %>% 
  mutate(`Thrombocytopenia_21d` = case_when(
    `Plt day +21` < 143                                             ~ "YES"
  )) %>% 
  mutate(`Thrombocytopenia_30d` = case_when(
    `Plt day +30` < 143                                             ~ "YES"
  )) %>% 
  mutate(`Thrombocytopenia_90d` = case_when(
    `Plt day +90` < 143                                             ~ "YES"
  )) %>% 
  mutate(gr3_Thrombocytopenia_apheresis = case_when(
    `Plt apheresis` < 50                                           ~ "YES"
  )) %>% 
  mutate(`gr3_Thrombocytopenia_-5d` = case_when(
    `Plt day -5 (k/ul)` < 50                                        ~ "YES"
  )) %>% 
  mutate(`gr3_Thrombocytopenia_0d` = case_when(
    `Plt day 0 (k/uL)` < 50                                        ~ "YES"
  )) %>% 
  mutate(`gr3_Thrombocytopenia_7d` = case_when(
    `Plt day +7` < 50                                              ~ "YES"
  )) %>% 
  mutate(`gr3_Thrombocytopenia_14d` = case_when(
    `Plt day +14` < 50                                             ~ "YES"
  )) %>% 
  mutate(`gr3_Thrombocytopenia_21d` = case_when(
    `Plt day +21` < 50                                             ~ "YES"
  )) %>% 
  mutate(`gr3_Thrombocytopenia_30d` = case_when(
    `Plt day +30` < 50                                             ~ "YES"
  )) %>% 
  mutate(`gr3_Thrombocytopenia_90d` = case_when(
    `Plt day +90` < 50                                             ~ "YES"
  )) %>%

  mutate(`cytopenia_30d` = case_when(
    `WBC day +30` < 4 | 
      `ANC day +30` < 1.8 | 
      `Hb day +30` < 11.4 | 
      `Plt day +30` < 143                                             ~ "YES",
    TRUE                                                              ~ "NO"
  )) %>% 
  mutate(`gr3_cytopenia_90d` = case_when(
    `WBC day +90` < 2 | 
      `ANC day +90` < 1 | 
      `Hb day +90` < 8 | 
      `Plt day +90` < 50                                             ~ "YES",
    TRUE                                                              ~ "NO"
  ))

@@

# day 30 + MRD for figure
#table(tct$day30_response_revised, tct$MRD_status, useNA= "ifany")
#table(tct$day30_response_revised, tct$day30_response, useNA= "ifany")
#tct$ORR_MRD <- case_when(#tct$day30_response_revised== "SD" ~ "SD",
                         #tct$day30_response_revised== "PD" ~ "PD",
                         #tct$day30_response_revised== "MR" ~ "MR",
#                         tct$day30_response_revised== "PR" ~ "PR",
                         #tct$day30_response_revised== "PR" & tct$MRD_status== "Positive" ~ "PR and MRD-positive",
                         #tct$day30_response_revised== "PR" & is.na(tct$MRD_status) ~ "PR and MRD unknown",
#                         tct$day30_response_revised== "sCR" & tct$MRD_status== "Negative" ~ "sCR and MRD-negative",
#                         tct$day30_response_revised== "sCR" & tct$MRD_status== "Positive" ~ "sCR and MRD-positive")
#table(tct$ORR_MRD)
```

```{r}
## Labeling
var_label(cart1) <- list(Age = "Patient Age", agecat = "Patient Age - Categories", 
                         # bmicat = "BMI at apheresis - Normal, Overweight, Obese", 
                         tumor_burden = "Tumor burden", proteasome = "Refractory to Proteasome Inhibitors", 
                         immuno = "Refractory to Immunomodulators", doubleref = "Double refractory", 
                         tripleref= "Triple refractory", pentaref= "Penta refractory",
                         # bmicat2 = "BMI at apheresis - Normal vs. Overweight/Obese", 
                         CRS_any = "Any CRS", CRS_gradecat = "CRS Grade", 
                         ICANS_any = "Any ICANS", ICANS_gradecat = "ICANS Grade", cyto= "High risk cytogenetics", 
                         # `ECOG > or = 2? (Yes=1, No=0)` = "Deletion 17p at Infusion", 
                         `t(4:14) prior to CAR-T infusion (yes=1, no=0)` = "t(4:14) at Infusion", `t(14:16) prior to CAR-T infusion (yes=1, no=0)` = "t(4:16) at Infusion", 
                         `Prior auto SCT (yes=1, no=0)` = "Prior autoSCT", 
                         `Prior Allo SCT (Yes=1, No=0)` = "Prior alloSCT",
         # `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)` = "Prior BCMA-directed therapy ",
         `Extramedullary Disease? (yes=1, no=0)` = "Extramedullary disease", dara= "Refractory to Daratumumab"#,
         # best_response = "Best response in first 90 days"
         )

@@

## Table 1. Patient baseline characteristics
**Change Male Sex**
```{r}
cart1 %>% 
  distinct(MRN, .keep_all = TRUE) %>% 
  select(Age, agecat, male_sex, Sex,
         `Extramedullary Disease? (yes=1, no=0)`, 
         tumor_burden, `ECOG at LD (at baseline visit)`, `R-ISS at CAR-T Infusion`, cyto, 
         `Bridging Therapy (Yes=1, No=0)`,
         `Prior auto SCT (yes=1, no=0)`, `Prior Allo SCT (Yes=1, No=0)`,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)`,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`) %>% 
  tbl_summary(
    type = list(
    `Extramedullary Disease? (yes=1, no=0)` ~ "categorical",
    cyto ~ "categorical",
    `Bridging Therapy (Yes=1, No=0)` ~ "categorical",
    `Prior auto SCT (yes=1, no=0)` ~ "categorical",
    immuno ~ "categorical", proteasome ~ "categorical", dara ~ "categorical",
    doubleref ~ "categorical", tripleref ~ "categorical", pentaref ~ "categorical",
    `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)` ~"categorical"),

    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
    digits = all_continuous() ~ 1
    ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
```

## Table 2. Clinical outcomes
**organize response**
**best response**
```{r}
cart1 %>% 
  distinct(MRN, .keep_all = TRUE) %>% 
  select(#`BMI at apheresis`, 
         # `t(4:14) prior to CAR-T infusion (yes=1, no=0)`, `t(14:16) prior to CAR-T infusion (yes=1, no=0)`, 
    `Max CRS grade (0-5)`,
         # CRS_any, CRS_gradecat, 
    `Day of onset of CRS relative to infusion`,
         `Day of Max CRS (relative to infusion)`, `Duration of CRS (days)`,

    `Max ICANS (relative to infusion)`,
         # ICANS_any, ICANS_gradecat, 
    `Day of onset of ICANS relative to infusion`,
    `Day of Max ICANS (relative to infusion)`,
         `Duration of ICANS (days)`,

    `Steroid use (Yes=1, No=0)`, `Tocilizumab (Yes=1, No=0)`, `Anakinra (Yes=1, No=0)`,

         # `Infection (yes, no)`,
    `Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`,
    `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`

                             # `Baseline CRP`, `Max CRP`, `Baseline Ferritin`, `Max Ferritin`, `Cell Dose (million cells)`, 
                             # `LDH at Baseline`, 
                             # `LDH day +30`, `LDH day +90`#, 
                             # `B2 Microglobulin at Baseline`, `Day 30 B2 Microglobulin`, `Day 90 B2 Microglobulin`, `Cyclophosphamide Dose (mg)`, `Cyclophosphamide Actual Dose (mg/m2)`, `Fludarabine Total Dose (mg)`, `Fludarabine Actual Dose (mg/m2)`, `Fludarabine Dose Reduction`
                             ) %>% 
  tbl_summary(type = list(
    c(`Day of onset of CRS relative to infusion`, `Day of onset of ICANS relative to infusion`,
      `Day of Max ICANS (relative to infusion)`, `Duration of ICANS (days)`) ~ "continuous",
    c(`Steroid use (Yes=1, No=0)`, `Tocilizumab (Yes=1, No=0)`, `Anakinra (Yes=1, No=0)`) ~ "categorical"
  ),
            statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
            digits = all_continuous() ~ 1) %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
```
For responses make denominator evaluable patients
Patient who died or was lost to follow-up or had non-secretory disease would not be evaluable

## Table 3. Bone marrow biopsy findings
**make sure of the variables used then combine them**
```{r}
tbl1 <- cart1 %>% 
  distinct(MRN, .keep_all = TRUE) %>% 
  select(`marrow cellularity baseline`, `marrow cellularity baseline (%)`,
         `marrow CD138 baseline (%)`, `marrow fibrosis baseline`, `marrow dysplasia baseline`
  ) %>% 
  tbl_summary(type = list(
    c(#`marrow cellularity baseline (%)`, `marrow CD138 baseline (%)`, 
      `marrow fibrosis baseline`) ~ "continuous"
  ),
            statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
            digits = all_continuous() ~ 1) %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)

tbl2 <- cart1 %>% 
  distinct(MRN, .keep_all = TRUE) %>% 
  select(`marrow cellularity day +30`, `marrow % cellularity day +30`,
         `marrow %CD138 day +30`, `marrow fibrosis day +30`, `marrow dysplasia day +30`
  ) %>% 
  tbl_summary(#type = list(
  #   c(`marrow % cellularity day +30`, `marrow %CD138 day +30`, `marrow fibrosis day +30`) ~ "continuous"
  # ),
            statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
            digits = all_continuous() ~ 1) %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)

tbl3 <- cart1 %>% 
  distinct(MRN, .keep_all = TRUE) %>% 
  select(`marrow cellularity day +90`, `marrow % cellularity day +90`,
         `marrow %CD138 day +90`, `marrow fibrosis day +90`, `marrow dysplasia day +90`
  ) %>% 
  tbl_summary(#type = list(
  #   c(`marrow % cellularity day +90`, `marrow %CD138 day +90`, `marrow fibrosis day +90`) ~ "continuous"
  # ),
            statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
            digits = all_continuous() ~ 1) %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)

tbl_merge(list(tbl1, tbl2, tbl3), tab_spanner = c("Baseline", "Day 30", "Day 90"))
```

## Table 4. Supportive therapies and engraftment
**Fix the + and <**
```{r}
cart1 %>% 
  distinct(MRN, .keep_all = TRUE) %>% 
  select(`Need for G-CSF post infus (Yes, No)`, `First Day of GCSF`, `Last Day of GCSF`,
         `CD34 stem cell boost`, `Day of stem cell boost`, `Boost cell dose (million cells)`,
         `Engraftment Day`,
         `RBC transfusion within 7d post CART`, `Plt transfusion within 7d post CART`, 
         `RBC transfusion >7d post CART`, `Plt transfusion >7d post CART`,
         `Need for IVIG (Yes, No)`, `First day of IVIG`, `Last day of IVIG`
  ) %>% 
  tbl_summary(type = list(
    c(#`Last Day of GCSF`,
    `Day of stem cell boost`, `Boost cell dose (million cells)`) ~ "continuous"
  ),
            statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
            digits = all_continuous() ~ 1) %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
```

## Table S1. Apheresis and product characteristics
```{r}
cart1 %>% 
  distinct(MRN, .keep_all = TRUE) %>% 
  select(`Final collection volume (mL)`, `Whole blood processed (mL)`,
         `TBV processed`, `Access type`, `Final collection volume (mL)`,
         `Run time (min)`,
         `Time from apheresis to CAR-T infusion (days)`, `Total bags`,
         `Total dose volume (mL)`, `Total cell dose (million cells)`

  ) %>% 
  tbl_summary(type = list(c(`Total bags`) ~ "continuous"),
            statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
            digits = all_continuous() ~ 1) %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
```

## Table S2. Cytopenias following ide-cel
**Change %**
```{r}
tbl1 <- cart1 %>% 
  distinct(MRN, .keep_all = TRUE) %>% 
  select(`Leukopenia_apheresis`, `gr3_Leukopenia_apheresis`, 
         `Neutropenia_apheresis`, `gr3_Neutropenia_apheresis`, 
         `Anemia_apheresis`, `gr3_Anemia_apheresis`, 
         `Thrombocytopenia_apheresis`, `gr3_Thrombocytopenia_apheresis`
  ) %>% 
  tbl_summary(type = list(everything() ~ "dichotomous"),
            digits = all_continuous() ~ 1,
            missing = "no") %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
